Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-08 paper.tex
Lead in to our four key ideas.

She listens intently to a story about a princess named Nell.  Later, when
the girl has learned a little more, she will give the princess her own
name, ``Rahel,'' and change all the colors, but for now the green
book shows her pictures and asks her to trace shapes on the screen.

@@

As she traces the R, it comes to life and gallops across the screen.
\textit{``Run starts with R.  Roger the R Runs across the Red Rug.  He has a
dog named Rover.''}  Rover barks: \textit{``Ruff! Ruff!''}  The Princess asks,
\textit{``Can you find something Red?''} and Rahel uses the camera to
photograph her red boots. \textit{``Very good!  You are a smart girl!''}

@@

\section{Key Ideas}
The interaction design of the Nell system described above is inspired
by the ``Young Lady's Illustrated Primer'' in the Neal Stephenson
novel \textit{The Diamond Age}, from whose protagonist Nell takes its
name.\footnote{In a nod to Seymour Papert, Nell can also be read as an
acronym for ``Narrative Environment for Learning Learning.''}
Nell's design embodies four key ideas: it is a \textbf{Narrative}
interface which is \textbf{Personalized} for the child and uses
\textbf{Direct Interaction}.  Nell is \textbf{Growable}: it has a
``low floor and no ceiling'' to allow a child to master more
and more of the system as she grows.

% olpc context here?
\cite{chang:tinkrbook, flores:uruguay, idb:peru}
%context: english literacy, far from teachers & schools
\subsection{Narrative}
% excerpt of story model
\subsection{Personal}
% customization, renaming characters
\subsection{Direct interaction}
% handwriting as UI?
% motor skills
% photo of XO-3?
\subsection{Growable (``no ceiling'')}
% modular -- the story expands.
% excerpt of TurtleScript
% text read aloud initially

@@

\section{Related work}
\subsection{The Sugar Learning Environment}
% Sugar
%% customization
%% path through the educational material?
\subsection{Narrative computing}
% Reidl
\subsection{Storytelling}
% TinkRBooks

>>>>

She listens intently to a story about a princess named Nell.  Later, when
the girl has learned a little more, she will give the princess her own
name, ``Rahel,'' and change all the colors, but for now the green
book draws pictures for her and asks her to trace shapes on the screen.

@@

As she traces the R, it comes to life and gallops across the screen.
\textit{``Run starts with R.  Roger the R Runs across the Red Rug.  He has a
dog named Rover.''}  Rover barks: \textit{``Ruff! Ruff!''}  The Princess asks,
\textit{``Can you find something Red?''} and Rahel uses the camera to
photograph her red boots.

\textit{``Very good!  You are a smart girl!''}

@@

\section{Key Ideas}
The interaction design of the Nell system described above is inspired
by the ``Young Lady's Illustrated Primer'' in the Neal Stephenson
novel \textit{The Diamond Age}, from whose protagonist Nell takes its
name.\footnote{In a nod to Seymour Papert, Nell can also be read as an
acronym for ``Narrative Environment for Learning Learning.''}
Nell's design embodies four key ideas: it is a \textbf{Narrative}
interface using \textbf{Direct Interaction} which \textbf{Grows} with,
and is \textbf{Personalized} for, the child.

We believe the combination of these four key ideas provides a novel
experience which addresses some of the shortcomings of earlier
learning environments for children.  In this section we will discuss
our motivating core concepts, and in the next we will describe how
they are implemented in Nell.

%Section~\ref{sec:related} discusses related work.
%The final section will draw conclusions and describe future work.

\subsection{Narrative}
% excerpt of story model
\subsection{Personal}
% customization, renaming characters
\subsection{Direct interaction}
% handwriting as UI?
% motor skills
% photo of XO-3?
\subsection{Growable (``no ceiling'')}
% it has a ``low floor and no ceiling'' to allow a child to master more
% and more of the system as she grows.

% modular -- the story expands.
% excerpt of TurtleScript
% text read aloud initially

@@

\section{Related work}\label{sec:related}
% Nell focused on Literacy
% olpc context here?
\cite{chang:tinkrbook, flores:uruguay, idb:peru}
%context: english literacy, far from teachers & schools
\subsection{The Sugar Learning Environment}
% Sugar
%% customization
%% path through the educational material?
\subsection{Narrative computing}
% Reidl
\subsection{Storytelling}
% TinkRBooks
